manuscript

### 2019-02-01 manuscript/manuscript.Rmd
update manuscript and figures

---
title: "manuscript"
author: "Yuanning Li"
date: "10/17/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
bibliography: manuscript.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo=FALSE,
	dpi=300,
	cache=TRUE
	)
```
# Lamellibrachia genome
## Abstract

## Introduction
![](../figures/Picture1.png) 
**Fig 1.** *Lamellibrachia* from seep localities in Gulf of Mexico.

Considerabel debate persists concenring the evolutionary origins of siboglinids, owing to conflicting theories of its origins from fossil and molecular age estimates. Siboglinids have been claimed to be as old as 430 MYA based on fossil tubes found in the Silurian fossil vent communities [@little2002fossil], but molecular clock analyses suggest a much recent ( 50-126MYA) origin based on COI or 16S sequences [@little2003hydrothermal]. Recently, Late Cretaceous *Osedax* fossil traces on reptile falls provides a firm calibration point for the molecular clock of the siboglinids (~100MYA) [@danise2015bone]. Moreover, a detailed chemical and morphological analyses of tubes from the Figueroa deposits were made by vestimentiferans, which greatly extends the age of this lineage than previous molecular clock analyses [@georgieva2017identification].

@@

### Biological materials.
Adult *Lamellibrachia* *luymesi* specimens were collected from seep localities in the Mississippi Canyon at 754 m depth in Gulf of Mexico (N 28°11.58', W 89°47.94'), using the R/V Seward Johnson and Johnson Sea Link in October 2009. All samples were frozen at 80˚C following collection.

### Genome sequencing and assembly. 
Vestimentum tissue was dissected from one individual of worm, and high molecular weight genomic DNA was extracted using the DNeasy Blood & Tissue Kit (Qiagen) according to the manufacturer’s protocols. Sequencing a total of six paired-end or mate-pair genomic DNA libraries with insert sizes ranging from 180 bp to 7 kb were performed by The Genomic Services Lab at the Hudson Alpha Institute in Huntsville, Alabama on an Illumina HiSeq 2000 platform (see details in Table S1). Paired-end libraries (180 bp, 400 bp, 750 bp) were prepared using the 125 bp TrueSeq protocols, and mate-pair libraries (3-5 kbp, 5-7 kbp) were generated using the Illumina Nextera Mate Pair Library Kit followed by size selection. Moreover, a 10X sequencing library was constructed using the 10X Chromium protocol (10X genomics) at the Hudson Alpha Institute. The finished library was sequenced on an Illumina HiSeqX platform, using paired 151 bp reads with a single 8 bp index read.

Our workflow of genome assembly was shown in Fig. S1. Two The paired-end and 10X raw reads were checked using FastQC v0.11.5 [@andrews2010fastqc] and quality filtered (Q score >30) using Trimmomatic v0.36 [@bolger2014trimmomatic]. The estimation of genome size, level of heterozygosity and repeat contes of the Lamellibrachia genome was determined by analaysing the kmer histograms generated from the paired-end libraries using Jellyfish v2.2.3 [@marccais2011fast] and GenomeScope [@vurture2017genomescope] (Fig. S2). The Mate-pair reads were trimmed and sorted using NxTrim v0.3.1 [@o2015nxtrim] which can recgonize and trim the artificial Nextera mate-pair circulation adapters. Only reads from category "mp" (true mate-pair reads) and "unkonwn" (mostly large insert size reads) were used for downstream scaffolding anlaysis. Reads from "pe" (paired-end reads) and "se" (single ends) categories were discarded.

Given that high heterozygosity of *Lamellibrachia* genome, all reads were assembled using Platanus v1.2.4 [@kajitani2014efficient] with a kmer size of 32. Scaffolding was conducted by mapping Illumina paired-end and mate-pair reads to contigs genrated by Platanus using SSPACE v3.0 [@boetzer2014sspace]. Gaps in the scaffolds were then filled with GapCloser v1.12 [@luo2012soapdenovo2]. Redundant allele scaffods were further remvoed using Redundans v0.13c with default settings [@pryszcz2016redundans]. Genome assembly quality was assessed using QUAST v3.1 [@gurevich2013quast]. Completeness of obtained genome was assessed using BUSCO v3[@waterhouse2017busco] with Metazoa_odb9 database (978 busco genes).

### Transcripome assembly and analysis
Total RNA was extracted from the plume, vestimentum and trophosome tissue from the same indivdisual of *Lamellibrachia* spicemen using Trizol. RNA-seq of adult tissues from plume, vestimentum and trophosome was performed using Illumina HiSeq 2000 platform in Hudson Alpha. After quality checking and trimming of raw sequencing reads, transcripts were assembled de novo with Trinity. Transcript isoforms with high similarity (≥ 95%) were removed with CD-HIT-EST v4.7 [@li2006cd]. Transcript abundance was estimated with Bowtie v2.2.9 [@langmead2012fast] and RSEM v1.2.26 [@li2011rsem] by mapping reads back to the transcriptomic assembly based on transcripts per million (TPM). A tissue specifically expressed gene was defined as a gene that had over 75% of the total transcripts in a particular tissue based on TPM [@albertin2015octopus]. GO enrichment analysis was performed based on the GO annotation using PANNZER2 [@toronen2018pannzer2]. Statistically overrepresented GO terms of trophosome-specific genes were identifed using Lamellibrachia gene models as background with AgriGO [@du2010agrigo].

### Genome annotation. 
Our genome annotation workflow was shown in Fig. S3. Gene models of *Lamellibrachia* genome were constructed following the Funannotate pipeline 1.3.0 (https://github.com/nextgenusfs/funannotate). Briefly, repeptive regions in the *Lamellibrachia* genome were identified usning RepeatModeler v1.0.8 [@smit2008repeatmodeler] and were subsequently soft-masked using RepeatMasker v4.0.6 [@chen2004using]. RNA-Seq data from different tissue were leveraged to improve the accuracy of gene prediction. RNA-Seq data were assembled *de* *novo* into transcriptomes using Trinity v2.4.0 [@haas2013novo] and HISAT 2.1.0 [@kim2015hisat] was used to algin RNA-Seq reads to the *Lamellibrachia* assembly. Transcrptome assemblies were then passed to PASA pipeline v2.3.3 [@haas2003improving] to identify high quality gene models. The aligned RNA-Seq data wes used to train the *ab* *initio* gene predictions using AUGUSTUS v3.3 [@stanke2006augustus]. Protein alignements from the SwissProt database to "Lamellibrachia" assembly were generated using exonerate [@slater2005automated] and Trinity/PASA transcripts were aligned to the genome using Minimap2 v2.1 [@li2018minimap2]. The tRNA genes were identified using tRNAscan-SE v1.3.1 [@lowe1997trnascan]. Finally, EvidenceModeler 1.1.0 [@haas2008automated] was used to combine all the evidences of gene prediction from protein alignemnts, transcritp alignments, and *ab* *initio* predictions to construct high quality gene models. 
Finally, functional annotations of predicted gene models were analyzed using several curated databases. KEGG orthology was assinged using the KEGG Automatic Annotation server. Gene models were further annotated with domain structure and protein identity by InterProScan [@zdobnov2001interproscan] and SwissProt database, respectively. Secreted proteins were predicted using SignalP [@petersen2011signalp] and Phobius [@kall2007advantages] using InterProScan.

### Phylogenomics adn Molecular clock analysis
Analysis of siboglinid phylogeny was conducted from publically available 16 transcriptomic data in conjuction with *Lamellibrachia* proteome. Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to OGs, and supermatrix construction were conducted with Agalma [@dunn2013agalma]. The final analyses presented here contained 13 siboglinids and four outgroups based on current understanding of annelid phylogeny. Maximum likelihood analyses were performed in IQTree under the best-fitting models for associated partition schemes determined by Modelfinder implemented in IQTree 1.6.3 [@nguyen2014iq] with ultrafast bootstrapping of 1000 replicates.

For molecular clock analysis, a relaxed molecular clock with a lognormal distribution and a Yule tree model was used in BEAST 2 v2.5.1 [@bouckaert2014beast]. A calibration was placed on the node representing the most recent common ancestor (MRCA) of *Osedax* using a normal distribution with a mean of 100 MYA and a standard deviation of 10 following the findings of [@danise2015bone].Another calibrartion was placed on the node of MRCA of Serpulida and Sabellida using a normal distribution with a mean of 267 MYA [@sanfilippo2017first]. Molecular clock analyses with BEAST 2 consisted of two independent runs with 1 million MCMC generations sampled every 1000 generations. Convergence was checked and confirmed by comparing trace plots in Tracer making sure the effective sample size of each parameter was greater than 100 and that stationarity appeared to have been achieved. Log and tree fiels were combined using Logcombiner. A maximum clade credibility tree with mean heights was calculated using TreeAnnotater. The resulted time-calibrated tree was plotted using R package, phyloch, strap and OutbreakTools. Bayesian inference using a molecular clock resulted in identical branching patterns as analysis with IQTree.

>>>>

---
title: "manuscript"
author: "Yuanning Li"
date: "10/17/2018"
output:
  word_document: default
  html_document: default
  Table_document: default
bibliography: manuscript.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo=FALSE,
	dpi=300,
	cache=TRUE
	)
```
# Genomic clues of chemosynthetic symbiosis from deep-sea seep-living *Lamellibrachia*
Yuanning Li^1^,^2^\*, Michael G. Tassia^1^, Damien S. Waits^1^, Viktoria E. Bogantes^1^, Kyle T. David^1^, Kenneth M. Halanych^1^

^1^ Department of Biological Sciences & Molette Biology Laboratory for Environmental and Climate Change Studies, Auburn University

^2^ Department of Ecology and Evolutionary Biology, Yale University

\* Corresponding author, yuanning.li@yale.edu

## Abstract
Since the discovery of chemosynthetic symbiosis in hydrothermal vents and cold seeps, the genetic mechanism(s) of how organisms maintain the unique host-symbiont associations at the molecular level is still mostly unknown. The gutless tubeworm *Lamellibrachia* represents one of the longest-lived invertebrates and is widespread in many deep-sea cold seeps, providing an excellent model to study mechanisms like the association of chemosynthetic symbiosis, adaptation to extreme environments. However, the genomic and molecular evolutionary information of tubeworms is exceptionally scarce. Here, we present and characterize the genome of *Lamellibrachia* *luymesi*. We found genomic evidence that symbionts may compensate for the host's deficiency in amino acid biosynthesis. Unexpectedly, we found a large expansion of hemoglobin B1 genes - many of which also possess a free cysteine residue which is hypothesized to function in sulfide-binding. Moreover, we found no evidence that sulfide-binding mediated by zinc ions is conserved across tubeworms, suggesting the hemoglobin structure and the sulfide-binding mechanism is potentially more complex than previously thought. Our comparative analyses suggest the Toll-like receptor pathway may be essential to host immunity and tolerance/sensitivity to symbionts and pathogens. Last, we identified and compiled several genes potentially play an important role in longevity. Thus, these results help elucidate previously unknown links and potential mechanisms related to the evolution of holobionts, adaptations to chemosynthetic environments, and likely extend to other chemosynthetic holobionts.

## Introduction

![](../figures/Figure1_animal.png)

**Figure 1.** *Lamellibrachia* from seep localities in the Gulf of Mexico.

Since their discovery in the 1980s, siboglinid tubeworms at hydrothermal vents and cold seeps have fascinated evolutionary biologists with their unique symbioses between the worms and chemosynthetic endosymbionts. However, the genetic underpinnings of how organisms maintain the host-symbiont associations at the cellular level are still mostly unknown. The vestimentiferan tubeworm *Lamellibrachia* *luymesi* is distributed along the Gulf of Mexico and is one of the most dominant taxa living in deep-sea cold seeps. At some seeps the vestimentiferan tubeworms are so abundant that they form a unique habitat that is attractive for other species (Fig 1), maintaining alpha and beta biodiversity and facilitating adaptive radiations and evolutionary novelties. Siboglinids typically lack a digestive tract and rely on sulfide-oxidizing bacterial symbionts for nutrition. Hosts acquire their symbionts from the surrounding environment and store them in a specialized tissue called the trophosome [@nussbaumer2006horizontal]. Previous studies suggested that vestimentiferan chemoautotrophic symbionts can use both reverse TCA cycle (rTCA) and the Calvin cycle for carbon fixation as a nutrient source for the hosts [@markert2007physiological, @li2018endosymbiont]. However, previous metabolic and physiological studies primarily focus on symbionts associated with tubeworm host lineages, and studies on how exchanges of nutritions and metabolites between two partners from the host's perspective are still lacking.

One of the key adaptations contributing to the remarkable ability of tubeworms to thrive in chemosynthetic habitats is the ability for siboglinid hemoglobins (Hbs) to bind oxygen and sulfide simultaneously and reversibly at two different sites [@zal1996multi]. To avoid the toxicity of sulfide while transferring it to their chemoautotrophic symbionts, siboglinids possess a multi hemoglobin system with three different extracellular hemoglobins (Hbs; V1, V2, and C1): two dissolved in the vascular blood, V1 and V2, and one in the coelomic fluid, C1 [@arp1981blood, @zal1996multi]. Siboglinid Hbs consist of four heme-containing chains (A1, A2, B1, B2).  Sulfur-binding capabilities are hypothesized to be due to free cysteine residues at key positions in Hbs, especially in the A2 and B2 chains [@zal1997primary]. V1 Hb can form persulfide groups on its four linker chains (L1-L4), a mechanism that can account for the higher sulfide-binding potential of this Hb [@zal1997primary]. However, another study found no evidence of the free cysteine hypothesis and suggested sulfide-binding affinity was mediated by the zinc moieties bound to amino acid residues at the interface between pairs of A2 chains in *Riftia* [@flores2005sulfide]. Thus, it is still not clear which mechanism is primarily responsible for sulfide-binding in siboglinids.

In contrast to the rapidly growing vent-living vestimentiferans [@lutz1994rapid], seep-living vestimentiferans are thought to be the most long-lived non-colonial marine invertebrates (up to 250 year to grow up to two meters) [@bergquist2000longevity]. Immunity is a critical evolutionary driver of maintaining symbiosis [@chu2013innate], has important implications in aging [@quesada2018giant], and is also potentially important for organisms being held in high densities in chemosynthetic environments. However, very little is known about genetic mechanisms related to immunity in most chemosynthetic host species, and it is far more complex in some groups of invertebrates than traditionally recognized from recent studies [@halanych2014repurposed] [@tassia2017toll]. Thus, *Lamellibrachia* provides an excellent model to study immunity function associated with host-symbiont relationships and adaptations to chemosynthetic habitats. However, the genomic and molecular evolution information on extremophile immunity and/or immune tolerance is exceptionally scarce.

Considerable debate persists concerning the evolutionary origins of siboglinids, owing to conflicting theories of its origins from fossil and molecular age estimates. Siboglinids have been claimed to be as old as 430 MYA based on fossil tubes found in the Silurian fossil vent communities [@little2002fossil], but molecular clock analyses suggest a more recent (50-126 MYA) origin based on mitochondrial *COI* or *16S* gene sequences [@little2003hydrothermal]. Recently, Late Cretaceous *Osedax* fossil traces on reptile falls provided a solid calibration point for the molecular clock of the siboglinids (~100 MYA) [@danise2015bone]. Moreover, a detailed chemical and morphological analyses of tubes from the Figueroa deposits suggested they were made by vestimentiferans, which significantly extends the age of this lineage to a Mesozoic origin than previous molecular clock analyses [@georgieva2017identification].

Here, we describe and investigate the genomic, transcriptomic and proteomic sequencing and comparative genomic analysis of tubeworm *Lamellibrachia* *luymesi* collected from the Gulf of Mexico. Our comparative genomic analyses of *Lamellibrachia* provide genomic evidence for genetic pathway and novel candidate genes which may underlie the extraordinary characteristics of tubeworms, including nutrition mode, hemoglobin evolution, immunity function and longevity. Moreover, we also conducted a detailed molecular clock analysis to discern among the hypotheses posed by previous debates concerning the evolutionary origins of siboglinids. Our findings provide hitherto previously unknown evidence of genetic machinery related to tubeworm success in deep-sea chemosynthetic communities, such as vents and seeps.

@@

## NCBI Accession

### Biological materials.
Adult *Lamellibrachia* *luymesi* specimens were collected from seep localities in the Mississippi Canyon at 754 m depth in the Gulf of Mexico (N 28°11.58', W 89°47.94'), using the R/V Seward Johnson and Johnson Sea Link in October 2009. All samples were frozen at 80˚C following collection.

### Genome sequencing and assembly.
Vestimentum tissue was dissected from one individual, and high molecular weight genomic DNA was extracted using the DNeasy Blood & Tissue Kit (Qiagen) according to the manufacturer’s protocols. Sequencing of six paired-end or mate-pair genomic DNA libraries with insert sizes ranging from 180 bp to 7 kb were performed by The Genomic Services Lab at the Hudson Alpha Institute in Huntsville, Alabama on an Illumina HiSeq 2000 platform (see details in Table S1). Paired-end libraries (180 bp, 400 bp, 750 bp) were prepared using the 125 bp TrueSeq protocols, and mate-pair libraries (3-5 kbp, 5-7 kbp) were generated using the Illumina Nextera Mate Pair Library Kit followed by size selection. Moreover, a 10X sequencing library was constructed using the 10X Chromium protocol (10X genomics) at the Hudson Alpha Institute. The finished library was sequenced on an Illumina HiSeqX platform, using paired 151 bp reads with a single 8 bp index read.

Our genome assembly workflow is shown in Fig. S1. The paired-end and 10X raw reads were checked using FastQC v0.11.5 [@andrews2010fastqc] and quality filtered (Q score >30) using Trimmomatic v0.36 [@bolger2014trimmomatic]. The estimation of genome size, level of heterozygosity, and repeat contents of the *Lamellibrachia* genome was determined by analyzing the kmer histograms generated from the paired-end libraries using Jellyfish v2.2.3 [@marccais2011fast] and GenomeScope [@vurture2017genomescope] (Fig. S2). The mate-pair reads were trimmed and sorted using NxTrim v0.3.1 [@o2015nxtrim] which can recognize and trim the artificial Nextera mate-pair circulation adapters. Only reads from category "mp" (true mate-pair reads) and "unknown" (mostly large insert size reads) were used for downstream scaffolding analysis. Reads from "pe" (paired-end reads) and "se" (single ends) categories were discarded.

Given the high heterozygosity of the *Lamellibrachia* genome, all reads were assembled using Platanus v1.2.4 [@kajitani2014efficient] with a kmer size of 32. Scaffolding was conducted by mapping Illumina paired-end and mate-pair reads to contigs generated by Platanus using SSPACE v3.0 [@boetzer2014sspace]. Gaps in the scaffolds were then filled with GapCloser v1.12 [@luo2012soapdenovo2]. Redundant allele scaffolds were further removed using Redundans v0.13c with default settings [@pryszcz2016redundans]. Genome assembly quality was assessed using QUAST v3.1 [@gurevich2013quast]. Completeness of obtained genome was assessed using BUSCO v3[@waterhouse2017busco] with Metazoa_odb9 database (978 Busco genes).

We also used

### Transcriptome assembly and analysis
Total RNA was extracted from the the plume, vestimentum and trophosome tissue from the same individual of *Lamellibrachia* using Trizol. RNA-Seq of adult tissues from plume, vestimentum, and trophosome was performed using Illumina HiSeq 2000 platform at Hudson Alpha as described above. After quality checking and trimming of raw sequencing reads, transcripts were assembled de novo with Trinity. Transcript isoforms with high similarity (≥ 95%) were removed with CD-HIT-EST v4.7 [@li2006cd]. Transcript abundance was estimated with Bowtie v2.2.9 [@langmead2012fast] and RSEM v1.2.26 [@li2011rsem] by mapping reads back to the transcriptomic assembly based on transcripts per million (TPM). A tissue-specifically expressed gene was defined as a gene that had over 75% of the total transcripts in a particular tissue based on TPM [@albertin2015octopus]. GO enrichment analysis was performed based on the GO annotation using PANNZER2 [@toronen2018pannzer2]. Statistically overrepresented GO terms of trophosome-specific genes were identified using *Lamellibrachia* gene models as background with AgriGO [@du2010agrigo].

### Proteomics characterization.
Proteomic analyses of *Lamellibrachia* trophosome tissue were performed by Proteomics & Metabolomics Facility at Colorado State University. Briefly, samples were transferred to 5mL tubes appropriate for use in the Bullet Blender Storm 5 (Next Advanced). Freshly cleaned, 3.2mm stainless steel beads were added at an approximate 1:1 sample: bead volume ratio (1-5 beads). The tissue/bead mixture was then combined with 1X PBS (Hyclone) spiked with 1X Halt Protease Inhibitor cocktail (Thermo Scientific) for an approximate 2:1 liquid: solid ratio (150-600μl). Tissue homogenization was achieved using speed setting 12 for 5 minutes. The stainless steel beads were removed and 0.1mm glass beads added at approximately 1:1 sample:bead ratio. Further homogenization was achieved at speed 8 for 3 minutes. Homogenate was then transferred to 1.5mL microcentrifuge tubes and subjected to cup horn sonication (Amplitude 70, 10s pulse, 20s off, 7 minutes total exposure time; Qsonica) while suspended in ice water. Insoluble material was pelleted by brief centrifugation at 3000xg. The resulting supernatant was subjected to protein quantification by the Pierce BCA Protein Assay Kit (ThermoFisher-Pierce) following manufacturer’s instructions. Absorbance of reacted samples was measured at 550nm and protein quantification stemmed from a quadratic fit of the Bovine Serum Albumin (BSA) standard curve.

50 μg total protein was aliquoted from each sample and processed for in-solution trypsin digestion as previously described (Schauer et al. 2013). A total of 0.5μg of peptides were then purified and concentrated using an on-line enrichment column (Waters Symmetry Trap C18 100Å, 5μm, 180 μm ID x 20mm column). Subsequent chromatographic separation was performed on a reverse phase nanospray column (Waters, Peptide BEH C18; 1.7μm, 75 μm ID x 150mm column, 45°C) using a 90 minute gradient: 5%-30% buffer B over 85 minutes followed by 30%-45%B over 5 minutes (0.1% formic acid in ACN) at a flow rate of 350 nanoliters/min. Peptides were eluted directly into the mass spectrometer (Orbitrap Velos Pro, Thermo Scientific) equipped with a Nanospray Flex ion source (Thermo Scientific) and spectra were collected over a m/z range of 400–2000 under positive mode ionization. Ions with charge state +2 or +3 were accepted for MS/MS using a dynamic exclusion limit of 2 MS/MS spectra of a given m/z value for 30 s (exclusion duration of 90 s). The instrument was operated in FT mode for MS detection (resolution of 60,000) and ion trap mode for MS/MS detection with a normalized collision energy set to 35%. Compound lists of the resulting spectra were generated using Xcalibur 3.0 software (Thermo Scientific) with a S/N threshold of 1.5 and 1 scan/group.

Tandem mass spectra were extracted, charge state deconvoluted and deisotoped by ProteoWizard MsConvert (version 3.0). Spectra from all samples were searched using Mascot (Matrix Science, London, UK; version 2.6.0) against gene models of *Lamellibrachia* host and symbiont genomes (derived from [@li2018endosymbiont]) assuming the digestion enzyme trypsin. Mascot was searched with a fragment ion mass tolerance of 0.80 Da and a parent ion tolerance of 20 PPM. Oxidation of methionine and carbamidomethyl of cysteine were specified in Mascot as variable modifications. Search results from all samples were imported and combined using the probabilistic protein identification algorithms [@keller2002empirical] implemented in the Scaffold software (version Scaffold_4.8.4, Proteome Software Inc., Portland, OR) [@searle2008improving]. Protein identifications were accepted if they could be established at greater than 99.0% probability and contained at least 1 identified peptide. Protein probabilities were assigned by the Protein Prophet algorithm [@nesvizhskii2003statistical]. Proteins that contained similar peptides and could not be differentiated based on MS/MS analysis alone were grouped to satisfy the principles of parsimony.

### Genome annotation.
Our genome annotation workflow is shown in Fig. S3. Gene models of the *Lamellibrachia* genome were constructed following the Funannotate pipeline 1.3.0 (https://github.com/nextgenusfs/funannotate). Briefly, repetitive regions in the *Lamellibrachia* genome assembly were identified using RepeatModeler v1.0.8 [@smit2008repeatmodeler] and were subsequently soft-masked using RepeatMasker v4.0.6 [@chen2004using]. RNA-Seq data from different tissue were leveraged to improve the accuracy of gene prediction. RNA-Seq data were assembled *de* *novo* into a single transcriptome using Trinity v2.4.0 [@haas2013novo] and HISAT 2.1.0 [@kim2015hisat] was used to align  RNA-Seq reads to the *Lamellibrachia* genome assembly. the transcriptome assembly was then passed to the PASA pipeline v2.3.3 [@haas2003improving] to identify high-quality gene models. The aligned RNA-Seq data was used to train the *ab* *initio* gene predictor using AUGUSTUS v3.3 [@stanke2006augustus]. Protein alignments from the SwissProt database to *Lamellibrachia* assembly was generated using exonerate [@slater2005automated] and Trinity/PASA transcripts were aligned to the genome using Minimap2 v2.1 [@li2018minimap2]. The tRNA genes were identified using tRNAscan-SE v1.3.1 [@lowe1997trnascan]. Finally, EvidenceModeler 1.1.0 [@haas2008automated] was used to combine all the evidence of gene prediction from protein alignments, transcript alignments, and *ab* *initio* predictions to construct high-quality consensus gene models. Functional annotations of predicted gene models was performed using several curated databases: KEGG orthology was assigned using the KEGG Automatic Annotation server [@moriya2007kaas]. Gene models were further annotated with domain structure and protein identity by InterProScan [@zdobnov2001interproscan] and SwissProt database, respectively. Secreted proteins were predicted using SignalP [@petersen2011signalp] and Phobius [@kall2007advantages] using InterProScan.

### Gene family analysis
Following all-to-all Diamond v1.0 [@buchfink2014fast] BLASTP searches against 22 selected lophotrochozoan proteomes (Table S2), orthology groups (OGs) were identified using Orthofinder with a default inflation parameter (I=1.5). Gene ontology annotation was performed using PANTHER v13.1 [@mi2016panther] with the PANTHER HMM scoring tool (pantherScore2.pl). Gene family expansion and contraction was estimated using CAFÉ v2.1 [@de2006cafe]. For each gene family, CAFÉ generated a family-wide P value, with a significant *P* value indicating a possible gene-family expansion or contraction event as suggested in the manual. Significantly expanded gene families (*p* < 0.05)were then classified by InterProscan.

In addition to the above gene family expansion or contraction analysis, the protein-coding sequences were used for discovery of genes under positive selection in from *L*. *luymesi* in comparison with selected lophotrochozoan species (including *Capitella* *teleta*, *Lottia*  *gigantea*, *Helobdella* *robusta*, *Octopus*  *bimaculoides*, *Crassostrea*  *virginica*, *Notospermus* *geniculatus* and *Phoronis* *australis*) using PosiGene, which is an automated pipeline for genome-wide detection of positively selected genes , with default settings (p < 0.05). In this positive selection analysis through the PosiGene pipeline, *L*. *luymesi* was used as the reference and anchored species for ortholog assignment of each OG.

### Manual annotation of gene families with potential interest.
In addition to the automatic annotation process mentioned above, we manually annotated genes that are general interest, such as hemoglobin gene families, genes related to amino acid synthesize, immunity function or longevity. These genes were specifically selected *a* *priori* based on our experience after a revision of the available publications in the field. For hemoglobin genes, datasets used for Hb gene family analyses, identified homologs, and their respective accession numbers are available in Fig. S# .Hbs and linker sequences of interest were obtained from *Lamellibrachia* genome and assembled siboglinid transcriptomes (see molecular clock analysis below) via diamond blastp (evalue cutoff 1E-5) by utilizing Hb and linker sequences acquired from GenBank of siboglinids as databases (Figure #). Sequences with best hits to target proteins were annotated for protein domain architecture using the Pfam databases included in InterProscan. After manual removal of redundant and incorrect sequences (e.g., sequences are too short or lack of globin domain), we used MAFFT 7.2.15 [@katoh2013mafft] to align Hb amino acid sequences. Maximum likelihood analyses were performed in IQTree under the best-fitting models for associated partition schemes determined by Modelfinder implemented in IQTree with ultrafast bootstrapping of 1000 replicates.

Our analysis for immunity-related genes largely follows the same workflow as used for Hbs, but instead were processed through the Extract_Homologs2 script used in [@tassia2017toll] (available at https://github.com/mtassia/Homolog_identification). Target proteins are available in Table S#. Importantly, the Extract_Homologs2 script identifies unique protein sequences within an animo acid dataset which fall within user-defined domain architecture criteria (Table S#+1). Due to this stringency, the pipeline identifies the complement of unique proteins for any target family, not the number of synonymous genes encoded in a genome.  Full amino acid sequences for TLRs were placed in a phylogenetic context using the bioinformatic workflow delineated above for Hbs.

Genes related to amino acids synthesis from *Lamellibrachia*, *Lamellibrachia* symbionts, and *Capitella* *teleta* genomes were performed by using the KEGG2 KAAS genome annotation web server and then visualized by the KEGG Mapper Reconstruct Pathway too. A BLASTp search of protein sequences from the genome annotation were queried against the Swiss-Prot database was used to search and supplement for proteins that were missing in the visualized KEGG pathway (Table S#).

### Phylogenomics and Molecular clock analysis
Analysis of siboglinid phylogeny was conducted utilizing from publically available transcriptomic datasets (n=16) in conjunction with our newly generated*Lamellibrachia* proteome (Table S3). Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to OGs, and supermatrix construction were conducted with Agalma [@dunn2013agalma]. The final analyses presented here contained 13 siboglinids and four outgroups based on current understanding of annelid phylogeny. Maximum likelihood phylogenetic reconstructions were performed in IQTree under the best-fitting models for associated partition schemes determined by Modelfinder implemented in IQTree 1.6.3 [@nguyen2014iq] with ultrafast bootstrapping of 1000 replicates (Fig. S#).

For the molecular clock analysis, a relaxed molecular clock with a lognormal distribution and a Yule tree model was used in BEAST 2 v2.5.1 [@bouckaert2014beast]. A calibration was placed on the node representing the most recent common ancestor (MRCA) of four *Osedax* species using a normal distribution with a mean of 100 MYA and a standard deviation of 10 following the findings of [@danise2015bone]. Another calibration was placed on the node of MRCA of Serpulida and Sabellida using a normal distribution with a mean of 267 MYA [@sanfilippo2017first]. Molecular clock analyses with BEAST 2 consisted of two independent runs with 1 million MCMC generations sampled every 1000 generations. Convergence was checked and confirmed by comparing trace plots in Tracer ensuring the effective sample size of each parameter was greater than 100 and that stationarity appeared to have been achieved. Log and tree files were combined using Logcombiner. A maximum clade credibility tree with mean heights was calculated using TreeAnnotater. The resulting time-calibrated tree was plotted using R packages, including phyloch, strap, and OutbreakTools. Bayesian inference using a molecular clock resulted in identical branching patterns as analysis with IQTree.

## Results and Discussion

### Genome features
The genome of *Lamellibrachia* was sequenced using a combination of Illumina paired-end, mate-pair, and 10x techniques. Results from high-throughput sequencing and genome assembly for *Lamellibrachia* are presented in Table S3 with at least 300 fold coverage using a combination of Illumina paired-end, mate-pair and 10X genomic sequencing with a variety of insert sizes. The haploid genome assembly size is ~687 Mb, similar to the result of  genome size estimation using GenomeScope (~646 Mb) (Fig. S2). The N50 value of the assembled scaffolds and contigs is 373 Kb and 24 Kb, respectively. Although N50 lengths and assembly quality of *Lamellibrachia* are comparable to those of other annelids (e.g. *Capitella* *teleta*, *Helobdella* *robusta*) (Table S4), the overall genome completeness measured by BUSCO (~ 95%) is one of the highest among other lophotrochozoans (Table S5), indicating the completeness of the genome assembly. With the support of RNA-seq data from different tissues, we estimated *Lamellibrachia* genome contains 38,998 gene models. The genome also exhibits a similar level of heterozygosity (0.6%) and repetitive contents (36.92%), compared to other lophotrochozoan genomes. The repeat contents of *Lamellibrachia* genome is shown in Table S6. We found 94 OGs appear to have undergone a genomic expansion compared to other lophotrochozoan genomes (Table S8).

### Nutritional adaptations to a symbiotic life stage
![](../figures/Figure2_nutrition.png)

**Figure 2.** *Lamellibrachia* lacks many genes related to amino acid biosynthesis. (A) Genes present in *Lamellibrachia* symbiont and *Capitella* *teleta* genomes but absent in *Lamellibrachia* genome. (B) Example of Lysine biosynthesis pathway in *Lamellibrachia*. Red boxes represent missing genes in the pathway.

Adult *Lamellibrachia* worms lack a digestive tract and rely solely on endosymbionts for nutrition. Noticeably, only 57 genes associated with amino acid biosynthesis were found in the *Lamellibrachia* host genome, of which eight were identified as proteins (Supplementary Data 1), whereas 90 genes were identified in *Capitella* genome (Fig. 2A). In contrast, the genome of the *Lamellibrachia* symbiont (110 genes) contains an essentially complete gene sets for the biosynthesis of all 20 proteinogenic amino acids and of 11 vitamins/cofactors. The lack of 30 genes related amino acid synthesis in *Lamellibrachia* compared to *Capitella* genome are involved in the biosynthesis of 13 out of 20 amino acids (e.g. five key enzymes in the Lysine biosynthesis pathway Fig. 2B).  As amino acids are indispensable for protein biosynthesis in the host, the sparse presence of amino acid synthesis-related genes in *Lamellibrachia* genome may indicate that the host depends on its symbionts for supply with amino acids and cofactors. Moreover, we found a large gene expansion of nutrient uptake ABC transport protein-coding genes in *Lamellibrachia* compared with other lophotrochozoans (Table S7). These findings are consistent with previous biochemical analyses which suggest that *Riftia* is also dependent on its bacterial symbiont for the biosynthesis of polyamines that are important for host metabolism and physiology [@minic2003arginine]. Interestingly, a similar mechanism of overcoming host-deficiency in amino acid synthesis has also been suggested in thiotrophic vesicomyid symbioses of *Calyptogena* *magnifia* [@newton2008comparative] and vent mussel symbioses of *Bathymodiolus* *azoricus* [@ponnudurai2017metabolic]. These results emphasize the potential that host-deficiency in amino acid syntheses and exchanges of metabolites between two partners might to be a common strategy for chemosynthetic symbioses.

In addition to the immediate release of fixed carbon and provision of  amino acids by the symbionts, we have found proteomic evidence of a second possible nutritional mode - digestion of symbionts directly by the host, as showed by the detection of abundant host-derived digestive enzymes in the trophosome tissue (Table S9). Although previous observations indicated that symbiont could be digested by *Riftia* [@bright2000autoradiographic], the direct evidence and underlying genetic mechanisms related to symbiont digestion were not characterized. We identified fifteen the host proteins related to lysosomal proteases that were both highly expressed and detected as proteins in the trophosome tissue, such as *Saposin* and multi copies of *Cathepsin* (Table S9). Lysosomes contain an array of digestive enzymes used for protein degradation in eukaryotic cells and are thought to play an essential role in symbiont digestion of *Bathymodilus*. *azoricus* [@ponnudurai2017metabolic]. We additionally identified 19 major proteasome components as proteins in the trophosome tissue, indicating a potential role in protein degradation of symbiont digestion. Thus, our results suggest that lysosomal host proteases and proteasome may facilitate the degradation of symbiont proteins during symbiont digestion, and may play a role maintaining population load of symbionts within trophosome, or possibly both.
